\normalfont\documentclass[letterpaper,11pt]{article}
\usepackage{amsmath, amsfonts,amssymb,latexsym}
\usepackage{fullpage}
\usepackage{parskip}
\usepackage{flexisym}
\usepackage{algorithm}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pythonhighlight}
\usepackage{amsmath}
\usepackage{hyperref}
\begin{document}
\setlength{\parindent}{2ex}
\newcommand{\header}{
	\noindent \fbox{
	\begin{minipage}{6.4in}
  	\medskip
  	\textbf{CS 261 - Data Structure} \hfill \textbf{Spring 2017} \\[1mm]
  	\begin{center}
    	{\Large HomeWork 5} \\[3mm]
  	\end{center}
	\today \hfill \itshape{Liangjian Chen}
	\medskip
	\end{minipage}}
}
\newcommand{\RN}[1]{%
  \textup{\uppercase\expandafter{\romannumeral#1}}%
}
\bigskip
\header

\begin{enumerate}
\item [Problem 1]\textbf{Solution:}\par
there would be one tree with 64 nodes.
\item [Problem 2]\textbf{Solution:}\par
Let's say the potential function is $f(n) = cn\log n$. \par
Insert operation: $\log n + f(n + 1) - f(n) = \log n + c(n+1)\log n+1 - cn\log n = O(\log n)$\par
Delete operation: $\log n + f(n - 1) - f(n) = \log n + c(n-1)\log n-1 - cn\log n = O(1)$\par

\item [Problem 3]\textbf{Solution:}\par
For all even number $n$, $n$-element heap has a element with one child.\par
The child is lay on right most position of the last layer. This element would be on the top of his child.
\item [Problem 4]\textbf{Solution:}\par
Assume $n$,$m$ is the number of nodes and edges in a graph. When applying Dijkstra with $k$-ary heap. The time complexity is
$O(m\log_k n + nk\log_k n)$\par
Now, $n = 2^d, m = d2^{d-1}$, let's say $f(k) = d2^{d-1}\log_k 2^d + 2^dk\log_k 2^d$
\begin{flalign*}
	&f(k) = d2^{d-1}\log_k 2^d + 2^dk\log_k 2^d&\\
	&= d2^{d-1}\frac{\log_2 2^d}{\log_2 k} + 2^dk \frac{\log_2 2^d}{\log_2 k}\\
	&= \frac{d^22^{d-1} + kd2^{d}}{\log_2 k}\\
	&\text{Take deravative of $f(k)$}\\
	&f'(k) = \frac{d2^d\log_2 k - \frac{(d^22^{d-1} + kd2^{d})}{k\ln 2}}{\log_2^2 k}\\
	&\text{assume $f'(k) = 0$, obtain that}\\
	&\frac{d}{2} = k\ln k - k\\
	&\text{the solution of $k$ would give us the best bound}
\end{flalign*}
But what is the best bound? Appartently if we choose $k = d/2$, we can obtain a bound of $O(\frac{d^22^d}{\log d})$. Now I am going to approve this bound is same as the bound of best $k$. To achieve that, we need prove the following:

\begin{flalign*}
	&\text{for a constant $C$ and the best $k_0$ which follows $\frac{d}{2} = k_0\ln k_0 - k_0$, the following inequlity should holds:}&\\
	&\frac{d^22^{d-1} + k_0d2^{d}}{\log_2 k_0} \ge C \frac{d^22^d}{\log_2 d}&\\
	&C \le \min_d(\frac{\log d}{\log k_0} * \frac{d + 2k_0}{2d})\\
	&\frac{\log d}{\log k_0} * \frac{d + 2k_0}{2d} \ge \frac{\log d}{\log k_0} * \frac{1}{2} \ge \frac{1}{2}\\ 	
\end{flalign*}
Thus there is a constant $C < \frac{1}{2}$ to achieve this inequlity. Now we can say the best bound is indeed $O(\frac{d^22^d}{\log d})$.
\end{enumerate}
\end{document}
